### 2016-06-13 sec4_baseline.tex
Some more updates
Fighting

\begin{algorithm}
\caption{Temporal Replication and Mining}
\label{algo:trm_overview}
\begin{algorithmic}[1]
\Require list of $\langle t, S_t \rangle$ pairs
\State $R \gets (\lceil \frac{K}{L} \rceil -1)*G+2K$
\State {---Map Phase---}
\label{code:trm-map-start}
\ForAll{$\langle t, S_t \rangle$}
	\ForAll{$i \in 1...R$}
		\State emit a $\langle t-i, S_t \rangle$ pair
	\EndFor  
\EndFor
\label{code:trm-map-end}
\State {---Partition and Shuffle Phase---}
\label{code:trm-par-start}
\ForAll{$\langle t, S \rangle$ pair} 
\State group-by $t$, emit a $\langle t, Par_t\rangle$
\State where $Par_t = \{S_t, S_{t+1}, .. S_{t+R}\} $
\EndFor
\label{code:trm-par-end}
\State {---Reduce Phase---}
\label{code:trm-red-start}
\ForAll{$\langle t,Par_t \rangle$}
\State lineSweepMining($Par_t$)
\label{code:trm-red-end}
\EndFor
\end{algorithmic}
\end{algorithm}

As shown in Algorithm~\ref{algo:trm_overview}, the TRM algorithm contains
three steps. First, in the map phase, each snapshot is keyed 
with its timestamp (lines~\ref{code:trm-map-start}-\ref{code:trm-map-end}). 
Second, in the partition phase, every snapshot is grouped with its next 
$R$ snapshots to form a partition (lines~\ref{code:trm-par-start}-\ref{code:trm-par-end}). 
We will shortly discuss how the $R$ value is derived. 
Third, in the reduce phase, a line sweeping method is invoked 
to mine GCMP within each partition (lines~\ref{code:trm-red-start}-\ref{code:trm-red-end}). 
It is easy to see that this method replicates a snapshots at most $R$ times.
%\subsubsection{Temporal Replication Partition}
The replication factor $R$ is critical for the performance of TRM.
If the $R$ is large, the shuffle cost as well as the reduce cost would be high. 
On the contrary, if $R$ is small, valid patterns may
be missed out. In the Algorithm~\ref{algo:trm_overview}, the 
$R$ is chosen as $(\lceil \frac{K}{L} \rceil -1)*G+2K$. We will show
later the correctness of this value.

@@

\subsection{Correctness of TRM}
We prove the correctness of TRM from two aspects. First,
the choice of $R = (\lceil \frac{K}{L} \rceil -1)*G+2K$ would 
not miss out any valid patterns. Second, no false patterns
are reported in any partitions. We formalize these two 
properties as \emph{completeness} and \emph{soundness} as follows:

@@

Apparently, in TRM, replicating the entire trajectories (i.e., $R=\mathbb{|T|}$)
meets the \emph{soundness} and \emph{completeness} requirements. However, it burdens the network shuffle and limits the parallelism. We carefully chose $R = (\lceil \frac{K}{L} \rceil -1)*G+2K$ and use
the following theorem to state the correctness:

\begin{theorem}[Correctness of Replication]
\label{thm:replication_partition}
Temporal replication partition is sound and complete.
\end{theorem}z
\begin{proof}
The soundness of partition can be observed from the fact 
that each partition represents a consecutive segments of trajectories. 
Therefore patterns in a partition can be directly mapped 
back to original trajectories. For completeness, with a
valid pattern $P$, let $T'$ be the subsequence of $P.T$ which conforms to $K,L,G$ 
with the smallest length. Note that there could be many qualified $T'$s. 
Let the $i^{th}$ local-consecutive segment of $T'$ be $l_i$ and 
let the $i^{th}$ gap of $T'$ be $g_i$. Then, the size of $T'$ can 
be written as $\Sigma_i (l_i + g_i)$.  Since $T'$ conforms to $K,L,G$, 
then $2K \geq \Sigma_i (l_i) \geq K$, $l_i \geq L$, $g_i \leq G$. 
It follows: $\Sigma_i(l_i+g_i) \leq (\lceil \frac{K}{L} \rceil -1) *G+2K$. 
If every partition is of at least such a size, then $T'$ must be
captured by at least one of the partition. Thus, the pattern $P$ would 
be valid in that partition. This proves the completeness.
\end{proof}

\begin{example}
We illustrate the work flow of  TRM method using Figure~\ref{fig:trm} (c)(d) with $M=2, K=2, L = 2, G=2$. 
In Figure~\ref{fig:trm} (c), snapshots are combined into partitions with sizes equal to 
$(\lceil \frac{K}{L} \rceil-1) *G+2K = 4$. Then a line sweep method is performed in (d) 
for partition $1$. Each $C_i$ refers to the candidate set during sweeping snapshot $i$. 
Initially, $C_1$ contains patterns whose object set is in snapshot $1$.
As line sweeps, at snapshot $4$, since the timestamps of $\{o_1,o_2\}$ and $\{o_5,o_6\}$ 
are both $\{1,2,4\}$ which violate the $G$ constraint, 
thus the two candidates are removed from $C_4$. After all snapshots are swept, 
$\{o_3,o_4\}$ is the qualified pattern and is outputted.
\end{example}

>>>>

\begin{algorithm}
\caption{Temporal Replication and Mining}
\label{algo:trm_overview}
\begin{algorithmic}[1]
\Require list of $\langle t, S_t \rangle$ pairs
\State $R \gets (\lceil \frac{K}{L} \rceil -1)*G+2K-2$
\State {---Map Phase---}
\label{code:trm-map-start}
\ForAll{$\langle t, S_t \rangle$}
	\ForAll{$i \in 1...R$}
		\State emit a $\langle t-i, S_t \rangle$ pair
	\EndFor  
\EndFor
\label{code:trm-map-end}
\State {---Partition and Shuffle Phase---}
\label{code:trm-par-start}
\ForAll{$\langle t, S \rangle$ pair} 
\State group-by $t$, emit a $\langle t, Par_t\rangle$
\State where $Par_t = \{S_t, S_{t+1}, .. S_{t+R}\} $
\EndFor
\label{code:trm-par-end}
\State {---Reduce Phase---}
\label{code:trm-red-start}
\ForAll{$\langle t,Par_t \rangle$}
\State lineSweepMining($Par_t$)
\label{code:trm-red-end}
\EndFor
\end{algorithmic}
\end{algorithm}

As shown in Algorithm~\ref{algo:trm_overview}, the TRM algorithm contains
three steps. First, in the map phase, each snapshot is keyed 
with its timestamp (lines~\ref{code:trm-map-start}-\ref{code:trm-map-end}). 
Second, in the partition phase, every snapshot is grouped with its next 
$R$ snapshots to form a partition (lines~\ref{code:trm-par-start}-\ref{code:trm-par-end}). 
We will shortly discuss how the $R$ value is derived. 
Third, in the reduce phase, a line sweeping method is invoked 
to mine GCMP within each partition (lines~\ref{code:trm-red-start}-\ref{code:trm-red-end}). 
It is easy to see that this method replicates a snapshots at most $R$ times.
%\subsubsection{Temporal Replication Partition}
The replication factor $R$ is critical for the performance of TRM.
If the $R$ is large, the shuffle cost as well as the reduce cost would be high. 
On the contrary, if $R$ is small, valid patterns may
be missed out. In the Algorithm~\ref{algo:trm_overview}, the 
$R$ is chosen as $(\lceil \frac{K}{L} \rceil -1)*G+2K-2$. We will show
later the correctness of this value.

@@

\subsection{Correctness of TRM}
We prove the correctness of TRM from three aspects. First,
setting $R = (\lceil \frac{K}{L} \rceil -1)*G+2K -2$
would not miss any valid patterns. Second, no false patterns
are reported in any partitions. Third, the choice of $R$ is
minimum. We formalize the first two 
properties as \emph{completeness} and \emph{soundness} as follows:

@@

Apparently, in TRM, replicating the entire trajectories (i.e., $R=\mathbb{|T|}$)
meets the \emph{soundness} and \emph{completeness} requirements. However, it burdens the network shuffle and limits the parallelism. We prove in the following theorem 
that the minimum $R$ is $(\lceil \frac{K}{L} \rceil -1)*G+2K -2$ 
to ensure the correctness:

%We carefully chose $R = (\lceil \frac{K}{L} \rceil -1)*G+2K$ and use
%the following theorem to state the correctness:

\begin{theorem}[Correctness of Temporal Replication]
\label{thm:replication_partition}
The minimum $R$ to ensure sound and complete of the temporal replication 
is $(\lceil \frac{K}{L} \rceil -1)*G+2K -2$.
\end{theorem}z
\begin{proof}
The soundness of partition can be observed from the fact 
that each partition represents a consecutive segments of trajectories. 
Therefore patterns in a partition can be directly mapped 
back to original trajectories. 
For completeness, let $T'$ be the \emph{shortest} valid subsequence (wrt. $K,L,G$) 
of a valid sequence $T$. Let $R$ be the upper bound for all $T'$s among 
all possible valid sequence. It is easy to see that, under such a setting,
any valid sequence would be captured by one of the partitions in temporal
replication. This proves the completeness. Now, we compute the minimum value
of $R$ as follows:
$T'$ can be viewed as $n$ consecutive segments with sizes $l_1,..,l_n$
and $n-1$ gaps with sizes $g_1,...,g_{n-1}$. Therefore $R$ is formulated 
as follows:
\begin{equation}
R = \max_{n} \{ \Sigma_{i=1}^{i=n} l_i + \Sigma_{i=1}^{i=n-1} g_i \}
\end{equation}
With the following constraints: (1)$\forall l_i, L \leq l_i \leq K-1$;(2)
$\forall g_i, 1 \leq g_i \leq G$; (3) $\Sigma_{i=1}^{i=n} l_i \geq K$ and
(4) $\Sigma_{i=1}^{i=n-1}l_i  \leq K-1$. The constraint (1)(2)(3) due to the 
validity of $T'$ and the constraint (4) is because of the minimum size of $T'$.
Observe that, constraints (1)-(4) form a convex polygon and $R$ is monotone
increasing wrt. $n$, the maximum value of $R$ is thus taken at the boundaries. Further
observe that $n \in [2, \lceil \frac{K}{L} \rceil]$ and $K \geq 1$, these
conditions naturally derive
$R = (\lceil \frac{K}{L} \rceil -1)*G+2K -2$.
%valid pattern $P$, let $T'$ be the subsequence of $P.T$ which conforms to $K,L,G$ 
%with the smallest length. Note that there could be many qualified $T'$s. 
%Let the $i^{th}$ local-consecutive segment of $T'$ be $l_i$ and 
%let the $i^{th}$ gap of $T'$ be $g_i$. Then, the size of $T'$ can 
%be written as $\Sigma_i (l_i + g_i)$.  Since $T'$ conforms to $K,L,G$, 
%then $2K \geq \Sigma_i (l_i) \geq K$, $l_i \geq L$, $g_i \leq G$. 
%It follows: $\Sigma_i(l_i+g_i) \leq (\lceil \frac{K}{L} \rceil -1) *G+2K$. 
%If every partition is of at least such a size, then $T'$ must be
%captured by at least one of the partition. Thus, the pattern $P$ would 
%be valid in that partition. This proves the completeness.
\end{proof}

\begin{example}
We illustrate the work flow of  TRM method using Figure~\ref{fig:trm} (c)(d) with $M=2, K=3, L = 2, G=2$. 
In Figure~\ref{fig:trm} (c), snapshots are combined into partitions with sizes equal to 
$(\lceil \frac{K}{L} \rceil-1) *G+2K - 2 = 4$. Then a line sweep method is performed in (d) 
for partition $1$. Each $C_i$ refers to the candidate set during sweeping snapshot $i$. 
Initially, $C_1$ contains patterns whose object set is in snapshot $1$.
As line sweeps, at snapshot $4$, since the timestamps of $\{o_1,o_2\}$ and $\{o_5,o_6\}$ 
are both $\{1,2\}$ which violate the $G$ constraint, 
thus the two candidates are removed from $C_4$. After all snapshots are swept, 
$\{o_3,o_4\}$ is the qualified pattern and is outputted.
\end{example}

### 2016-06-13 sec7_experiment.tex
Checkpoint
Saved algo part
Some more updates
Fighting

\section{Experimental Study}
\label{sec:experiment}
\subsection{Implementation Issues}
We use Apache Spark~\footnote{http://spark.apache.org/} as the experimental
platform. Spark is one of the most popular MapReduce-like platform which
uses in-memory cache to gain high speedup against Apache Hadoop~\cite{}. Since
Spark directly supports the MapReduce paradigm, our algorithm is able to 
be easily implemented in Spark. In order to help reproduce our experiments,
we further address some implementation issues.
\subsubsection{Task Assignment}
In spark, each task in reduce phase is an Apriori mining phase of 
a star.
Although our star partition method is theoretically balanced, 
it is still necessary to assign equal number of tasks to each executors. 
Spark naturally uses hashing to partition data into tasks, where such
a partitioning does not care on the tasks size. In order to
fully utilize the clusters, it is important to perform a weight-aware
partition. In our implementation, we collect the number of edges
in each star after map phase. Afterwards, we use a simple \emph{best-fit} strategy,
where we assign stars in decreasing order with their sizes and each star
is assigned to the currently least-loaded executor.  HERE WE MAY HAVE ANOTHER BOUND
FROM LITERATURE, BUT I DIDN'T FIND YET. The injection of load balancing strategy
between map and reduce phase can be naturally implemented in Spark, where the 
map result can be cached and the reduce phase can be paused until when the
partition strategy is ready.

\subsubsection{Duplication Detection}
It is notable that the patterns discovered from different tasks (stars) could
be redundant due to containment relationship. For example, a pattern $\{a,b,c\}$
can be discovered from the star $Sr_a$, while the pattern $\{b,c\}$ can be discovered
from the star $Sr_b$. Though in most applications, such a duplicate pattern
is permitted, we offer an option to eliminate these patterns. The strategy is 
to broadcast each reducers output to every other reducers. This can be
efficiently done via \emph{broadcast} variables~\footnote{http://spark.apache.org/docs/latest/programming-guide.html\#broadcast-variables} in Spark. Afterwards, each reduce can check 
whether any resulted patterns are subsumed and thus filter those patterns.
Theoretically, advanced techniques, such as Bloom Filters, can be applied to efficiently
deal with the duplication detection. However, as the number of final patterns are
normally quit small, we leave the exploration for those techniques to the future.

\subsubsection{Handling Overlapping Clusters}
When handling patterns such as \emph{flock} and \emph{group}, disk-based clustering
on objects are applied. Such a clustering method may result one object belonging to
multiple clusters. In such a case, just keeping the timestamps in the edge
of connection graph is insufficient. Instead, we extend every timestemp $t$
to a pair $\langle t,C \rangle$, where $C$ is the set of clusters objects
belong to at time $t$. The only adaption we need to take the join during
apriori phase. Given two timestamp set $T_1$ and $T_2$, the join result of
$T_1$ and $T_2$ instead of being $\{\forall t | t\in T_1 \wedge t_\in T_2\}$,
it changes to $\{\forall (t,C) | t\in T_1 \wedge t \in T_2 \wedge C = (T_1.C \cap T_2.C) \wedge C \neq \emptyset\}$.
It is obvious to see the \emph{edge simplification} and \emph{candidate pruning} 
still holds under this new setting.

@@

We setup HDFS on the same cluster and all trajectory data
are initially stored in the HDFS. We prepare two set of
large-scaled trajectories with the following properties:

>>>>

\section{Experimental Study}
\label{sec:exp}
\subsection{Implementation Issues}
We use Apache Spark~\footnote{http://spark.apache.org/} as the experimental
platform. Spark is one of the most popular MapReduce platform which
uses in-memory cache to gain high speedup against Apache Hadoop~\cite{}. 
Due to the direct support of MapReduce, our algorithm can be easily implemented in Spark. 
In order to help reproduce our experiments, we further address some implementation issues.
%\subsubsection{Task Assignment}
%In spark, each task in reduce phase is an Apriori mining phase of 
%a star.
%Although our star partition method is theoretically balanced, 
%it is still necessary to assign equal number of tasks to each executors. 
%Spark naturally uses hashing to partition data into tasks, where such
%a partitioning does not care on the tasks size. In order to
%fully utilize the clusters, it is important to perform a weight-aware
%partition. In our implementation, we collect the number of edges
%in each star after map phase. Afterwards, we use a simple \emph{best-fit} strategy,
%where we assign stars in decreasing order with their sizes and each star
%is assigned to the currently least-loaded executor.  HERE WE MAY HAVE ANOTHER BOUND
%FROM LITERATURE, BUT I DIDN'T FIND YET. The injection of load balancing strategy
%between map and reduce phase can be naturally implemented in Spark, where the 
%map result can be cached and the reduce phase can be paused until when the
%partition strategy is ready.
%
%\subsubsection{Duplication Detection}
%It is notable that the patterns discovered from different tasks (stars) could
%be redundant due to containment relationship. For example, a pattern $\{a,b,c\}$
%can be discovered from the star $Sr_a$, while the pattern $\{b,c\}$ can be discovered
%from the star $Sr_b$. Though in most applications, such a duplicate pattern
%is permitted, we offer an option to eliminate these patterns. The strategy is 
%to broadcast each reducers output to every other reducers. This can be
%efficiently done via \emph{broadcast} variables~\footnote{http://spark.apache.org/docs/latest/programming-guide.html\#broadcast-variables} in Spark. Afterwards, each reduce can check 
%whether any resulted patterns are subsumed and thus filter those patterns.
%Theoretically, advanced techniques, such as Bloom Filters, can be applied to efficiently
%deal with the duplication detection. However, as the number of final patterns are
%normally quit small, we leave the exploration for those techniques to the future.
%
%\subsubsection{Handling Overlapping Clusters}
%When handling patterns such as \emph{flock} and \emph{group}, disk-based clustering
%on objects are applied. Such a clustering method may result one object belonging to
%multiple clusters. In such a case, just keeping the timestamps in the edge
%of connection graph is insufficient. Instead, we extend every timestemp $t$
%to a pair $\langle t,C \rangle$, where $C$ is the set of clusters objects
%belong to at time $t$. The only adaption we need to take the join during
%apriori phase. Given two timestamp set $T_1$ and $T_2$, the join result of
%$T_1$ and $T_2$ instead of being $\{\forall t | t\in T_1 \wedge t_\in T_2\}$,
%it changes to $\{\forall (t,C) | t\in T_1 \wedge t \in T_2 \wedge C = (T_1.C \cap T_2.C) \wedge C \neq \emptyset\}$.
%It is obvious to see the \emph{edge simplification} and \emph{candidate pruning} 
%still holds under this new setting.

@@

The clusters is managed by Yarn 2.7.1 and we use HDFS
as the distributed storage. We prepare three real data
set as follows:
\begin{itemize}
\item{Geolife}:
\item{ACTShopping}:
\item{SingTaxi}:
\end{itemize}

The summary of statistics are presented as in the following table:

\begin{table}
\center
\caption{Statistics of data set}
\begin{tabular}{|c|c|c|c|}
\hline
 & Geolife & ACTShopping & SingTaxi \\ 
\hline 
\# objects & a & a & a\\ 
\hline
\# timestamps & a & a & a\\ 
\hline
\# data points & a & a & a\\ 
\hline
\end{tabular}
\end{table}

\subsection{Effectiveness of GCMP}

\subsection{Performance Comparison}
\subsubsection{Effects of clusters $\epsilon$, $minPt$}
\subsubsection{Effects of pattern parameters $M,L,K,G$}

\subsection{SPM Analysis}
\subsubsection{Load Balance}
\subsubsection{Scalability}
